Invasive lionfish present region-wide variation of allometric growth in the Western Atlantic

### 2018-05-09 docs/Manuscript.Rmd
Ups, forgot to stash and commit the discussion changes

The results presented in this paper can have major implications for management. Our results show that, for a given length, using one set of parameters or the other can result in a threefold increase in estimated weight. Using site-specific values provides a more accurate estimate of fish biomass. This becomes especially relevant when estimating biomass available for harvest, predicting effects on local ecosystems, or evaluating the effectiveness of removal programs. \citet{edwards_2014} simulated lionfish culling using parameters from North Carolina and Little Cayman, and identify that the difference in time required for the population to recover to 90% of its initial biomass after removals cease was of up to four years. Future research should try to use, to the extent possible, parameters calculated for their region, or use different parameters to provide upper and lower bounds in their results. At the same time, this highlights the need for more basic research that furthers our understanding of lionfish biology. To better manage the invasion, we must perform research that can describe biologically important information of lionfish throughout its invasion range \citep{johnson_2016}.

>>>>

The results presented in this paper can have major implications for management. For example, \citet{edwards_2014} simulate lionfish culling using parameters from North Carolina and Little Cayman, and identify that the difference in time required for the population to recover to 90% of its initial biomass after removals cease was of up to four years. Our results show that, for a given length, using one set of parameters or the other can result in a threefold increase in estimated weight. This differences become especially relevant when estimating biomass available for harvest, predicting effects on local ecosystems, or evaluating the effectiveness of removal programs. Future research should try to use, to the extent possible, parameters calculated for their region, or use different parameters to provide upper and lower bounds in their results. At the same time, this highlights the need for more basic research that furthers our understanding of lionfish biology. To better manage the invasion, we must perform research that can describe biologically important information of lionfish throughout its invasion range \citep{johnson_2016}.

### 2018-05-09 docs/Manuscript.tex
Ups, forgot to stash and commit the discussion changes

The results presented in this paper can have major implications for
management. Our results show that, for a given length, using one set of
parameters or the other can result in a threefold increase in estimated
weight. Using site-specific values provides a more accurate estimate of
fish biomass. This becomes especially relevant when estimating biomass
available for harvest, predicting effects on local ecosystems, or
evaluating the effectiveness of removal programs. \citet{edwards_2014}
simulated lionfish culling using parameters from North Carolina and
Little Cayman, and identify that the difference in time required for the
population to recover to 90\% of its initial biomass after removals
cease was of up to four years. Future research should try to use, to the
extent possible, parameters calculated for their region, or use
different parameters to provide upper and lower bounds in their results.
At the same time, this highlights the need for more basic research that
furthers our understanding of lionfish biology. To better manage the
invasion, we must perform research that can describe biologically
important information of lionfish throughout its invasion range
\citep{johnson_2016}.

>>>>

The results presented in this paper can have major implications for
management. For example, \citet{edwards_2014} simulate lionfish culling
using parameters from North Carolina and Little Cayman, and identify
that the difference in time required for the population to recover to
90\% of its initial biomass after removals cease was of up to four
years. Our results show that, for a given length, using one set of
parameters or the other can result in a threefold increase in estimated
weight. This differences become especially relevant when estimating
biomass available for harvest, predicting effects on local ecosystems,
or evaluating the effectiveness of removal programs. Future research
should try to use, to the extent possible, parameters calculated for
their region, or use different parameters to provide upper and lower
bounds in their results. At the same time, this highlights the need for
more basic research that furthers our understanding of lionfish biology.
To better manage the invasion, we must perform research that can
describe biologically important information of lionfish throughout its
invasion range \citep{johnson_2016}.
